From physical principles to Hamiltonian mechanics

### 2014-06-30 2014ClassicalHamiltonianDerivation/classicalHamiltonianDerivation.tex
Changed position of citation.

To prepare for the limit we define $m(i)=w(i)/\bar{w}$\footnote{This $m(x)$ solves the same problems addressed by the invariant measure $m(x)$ introduced by Jaynes\cite{Jaynes}, which modifies Shannon's differential information entropy definition to be invariant under coordinate transformation\cite{Shannon}.}, where $\bar{w}$ represents the average width of the cells. We increase the number of the cells and reduce $\bar{w}$ while keeping $m(i)$ finite. In the limit we'll have a cell for each value, so we can use $x(i)$ (or simply $x$) instead of $i$ for the label. $\rho$ and $m$ will converge to functions defined over $x$. The corresponding configuration state will become $\mathbbm{c}_j=\int \rho(x) m(x) \mathbbm{s}_x dx$.

>>>>

To prepare for the limit we define $m(i)=w(i)/\bar{w}$\footnote{This $m(x)$ solves the same problems addressed by the invariant measure $m(x)$ introduced by Jaynes\cite{Jaynes}, which modifies Shannon's differential information entropy definition\cite{Shannon} to be invariant under coordinate transformation.}, where $\bar{w}$ represents the average width of the cells. We increase the number of the cells and reduce $\bar{w}$ while keeping $m(i)$ finite. In the limit we'll have a cell for each value, so we can use $x(i)$ (or simply $x$) instead of $i$ for the label. $\rho$ and $m$ will converge to functions defined over $x$. The corresponding configuration state will become $\mathbbm{c}_j=\int \rho(x) m(x) \mathbbm{s}_x dx$.
